Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-08-25 journal paper/code_abstract.tex
slight edits to abstract

\textbf{(i)}  
The most obvious decision rule (\HardMax) maximizes the Bayesian-expected reward. We find that \HardMax is not conducive to adopting better algorithms: each principal's dominant strategy is to choose the greedy algorithm. Further, we show that \HardMax is very sensitive to tie-breaking: if the tie-breaking is probabilistically biased in favor of one principal, then this principal has a simple ``winning strategy" no matter what the other principal does.

@@

>>>>

\textbf{(i)}  
The most obvious decision rule (\HardMax) maximizes the current agent's Bayesian-expected reward. We find that \HardMax is not conducive to adopting better algorithms: each principal's dominant strategy is to choose the greedy algorithm. Further, we show that \HardMax is sensitive to tie-breaking: if the tie-breaking is probabilistically biased in favor of one principal, then this principal has a simple ``winning strategy" no matter what.

@@

\xhdr{Significance.}
Our theory takes a Bayesian approach and discovers several strong asymptotic results. The numerical simulations provide a more nuanced and ``non-asymptotic" perspective. In essence, we look for substantial effects within relevant time scales. In fact, we start our investigation by determining what time scales are relevant in the context of our model. Our study has a dual purpose: (i) shed light on real-world implications of some typical scenarios, and (ii) investigate the space of models for describing the real world. As an example to clarify the latter point, consider the \HardMax model with simultaneous entry. It is is not necessarily the most realistic model. However, our results elucidate the need for more refined models that allow for ``free exploration" (\eg via random agents or early entry).
